MLExplain

### 2018-05-24 paper.tex

To interpret OCaml code, we need to parse it. However, our compiler does not
allow us to use the standard library nor an external one. Fortunately,
JSExplain itself did not trace the parsing process. That is why we have been
able to separate totally the parser from the interpreter and use another
compiler to compile it. The figure \ref{fig:archi} describes the architecture
of the whole application.

The parser is compiled with
\emph{js\_of\_ocaml} \cite{DBLP:journals/spe/VouillonB14}, the compiler of the
project \emph{Ocsigen}.

>>>>

To interpret OCaml code, we need to parse and type it. However, our compiler
does not allow us to use the standard library nor an external one. Fortunately,
JSExplain itself did not trace both parsing and typing processes. That is why
we have been able to separate totally the frontend from the interpreter itself
and use another compiler to compile it. The figure \ref{fig:archi} describes
the architecture of the whole application.

The frontend is compiled with \emph{js\_of\_ocaml}
\cite{DBLP:journals/spe/VouillonB14}, the compiler of the project
\emph{Ocsigen} \cite{balat:hal-00691710}.
